---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gnm

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/gnm)](https://cran.r-project.org/package=gnm)
[![Travis-CI Build Status](https://travis-ci.org/hturner/gnm.svg?branch=master)](https://travis-ci.org/hturner/gnm)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hturner/gnm?branch=master&svg=true)](https://ci.appveyor.com/project/hturner/gnm)

Functions to specify and fit generalized nonlinear models, including models with
multiplicative interaction terms such as the UNIDIFF model from sociology and 
the AMMI model from crop science, and many others.  Over-parameterized 
representations of models are used throughout; functions are provided for 
inference on estimable parameter combinations, as well as standard methods for 
diagnostics etc.

## Installation

You can install **gnm** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hturner/gnm")
```